%\chapter*{-overture-}
\onecolumn
{\LARGE
\ldots four days in the wild is enough to suck the strength out of you: no
sleep, bad food, bugs and rain. When those days are spent on the move,
allways looking over your shoulder for bandits or worse, they
can push you to the limits of exhaustion. We had two days to go
to reach Hanuma and deliver the package, and they were going to
be longer than we'd like.

Dinner is a snake we caught, roasted over the smallest fire in
the world  -- tasty, but rain had ruined the salt it really needed.
Then it was settling in for first watch. This is always a mixed
blessing: the hours just after sundown were the most dangerous
as far as the beasts were concerned but you got the best chunk
of sleep. Kyra could sleep anywhere, like she could just turn to
a puddle, catlike. Vitale was more like me, tossing fitfully
until exhaustion finally pulled him under. I added another stick
to the fire.

If you didn't know, the wilds have a sound to them: the brush of leaves, the
scuttling of beetles, crickets, bats, all the things out there.
There is nothing, however, like the peculiar deafening hush that falls
over it when something\ldots unnatural passes too close. See, your
brain doesn't really understand nothing, so instead of noticing
that the world has gone quiet, it first starts to jump at shadows, at
anything that it \emph{can} sense. Recognising it, I grabbed my axe and
screamed, hoping to wake the other two as I turned to face\ldots}
\twocolumn
\chapter{overview}
This is all about creating your character. Depending on your
style, your character could be a number of things to you. It
could be like a piece in a strategic game such as chess to be
moved as tactics dictate. It could be like a character in a
play, with yourself as actor. It could be your alter ego, your
self in the world of the game. Typically, it's some mix of the
three.

These rules are about how to create your character in the first place
and how they will evolve as they experience more of the world.
Built in to this is a natural progression. Those starting out
are considered still in training, not yet masters of their
chosen art. At some point, they will choose a more advanced
regimen, taking on a special path of attainments. Unusual or
driven individuals may find additional paths open to them as others
recognise their attainments.
