\documentclass[letterpaper, 12pt]{book}
\title{The Ring}
\author{Ryan Davis\\iconoclasmandheresy@gmail.com}
\usepackage{pxfonts}
\begin{document}
\maketitle
\frontmatter
\tableofcontents
\clearpage
\section{Introduction}
\mainmatter
\chapter{Setting}
\section{Terms}
\begin{description}
\item[Crystal:] Nearly ubiquitous quantum nanoparticles left by the Primordials.
\item[Primordials:] Vanished K-2 (K-3?) culture predating known history.
\end{description}
\section{History}
Perhaps the wrong term for this.
History is the events that have unfolded, and our story begins before that time.
Sometimes, it survives, distorted, as myth and legend.
More often, it was simply forgotten and new stories were invented to fill the obvious gaps left in the narrative.
So, before all that is known, the following is supposition, backed with evidence.
\subsection{Primordial Epoch}
Long ago, but not so long ago that relatively few new worlds have formed since then, there was a civilization that dominated the galaxy.
`Primordials' is the term used in this work, though `Progenitor', `Creators', `Gods', `Demons', and `Ancients' fit in their own way and are in use vy various Sub-Cultures.
Every world visited in a system past the 'Heavy Bombardment' stage of development with a solid crust shows sighs not only of having been visited but inhabited.
This puts the date of their disappearance between around 0.25-100 million years ago.
Many, tho not all, of those worlds show evidence of catastrophic transformations on planetary and in some cases system-wide scales.
K-2 levels of energy utilization are not unheard of in estimation of the power requirements in the most extreme examples.

Disappearance is perhaps the wrong word.
It is suspected that, due to underlying similarities in genetics and biochemistry, nearly all of the species making up The Cultures are descended from species manipulated by the Primordials if not the Primordials themselves.
What can be stated is that there was a rapid and disruptive transformation throughout the Primordial civilization that, combined with the passage of time, has destroyed whatever records they may have kept about themselves.
We, it seems, are the greatest of thir works to survive.

The second great legacy of the Primordials is Crystal, sub-micron scale machines that communicate using what are now poorly understood quantum principals.
We know, having examined remnants of their anima, they they were designed by what we can only assume are the Primordials to assist them in reshaping the galaxy.
\subsection{The Dark Epoch}
Between the fall of Primordial civilization and the various Cultures return to civilization is the Dark Epoch.
Archaeology tells different stories, of each Culture's re-emergence, how each rose to reclaim the stars.
The narrative is similar, enough so that we can generalize the pattern of survival, superstition, rediscovery, and eventual re-connection to the Transport.
\subsection{Re-emergance}
\section{Peoples and Cultures}
All of the peoples have a complex of design and co-evolution traits that allow them to interact with Crystal in some way, just as one expects any life-form to exploit the resources around it.
For some, this interaction is highly localized or focussed, such as the people classed as `warmachines' who incorporate them into their physical forms rendering them into resiliant, self-repairing, extremely touch physical specimens.
Others, like the 'clouds' extend their conciousness into all of the nearby Crystal, manipulating or even subverting its anima.
\end{document}
